---
title: "p8105_hw1_jv3014"
author: "Jia Varkey"
date: "2026-09-22"
output: github_document
---

## Problem 1
```{r echo = F, message = F}
library(tidyverse)
data("penguins", package = "palmerpenguins")
penguins
```

The penguins data set includes size measurements for adult foraging penguins near Palmer Station Antarctica.
Important variables in this data set include 
It contains measurements for `r nrow(penguins)` penguins across `r ncol(penguins)` variables. 
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`
`
```{r}
# scatterplot

penguin_plot = ggplot(penguins, 
                      aes(x= bill_length_mm, y= flipper_length_mm, color = species)) + geom_point()

ggsave("penguin_plot.png")
```


## Problem 2

```{r}
set.seed(0)
data = tibble( 
  num_var = rnorm(10),
  log_var = num_var > 0,
  char_var = character(10),
  factor_var = factor(10, levels = 3)
  )

mean(pull(data,num_var))
mean(pull(data,log_var))

```
Calculating the mean works for the random sample and logical vector. It does not work for the character or factor vector since it is not numeric. 


```{r}
num_log = as.numeric(pull(data,log_var))
num_char = as.numeric(pull(data,char_var))
num_factor = as.numeric(pull(data,factor_var))
```

The logical vector returns numeric 0s and 1s, the character and factor vector return NA only.
This explains what happens when you try to take the mean of each variable because it cannot be calculated on non-numeric variables. 